---
title: "day 10 activity"
author: "Kiran Favre"
date: "2022-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(beeswarm)
library(ggplot2)
library(tvthemes)
library(ggthemes)
library(showtext)
font_add_google("Special Elite", family = "special")
```

```{r}
ice_duration_data <- read_csv(here("data", "ntl33_v7.csv"), na = "-999")


meteorological_data <- read_csv(here("data", "ntl20_v6.csv"))
```


Create a visualization that compares ice duration across different lakes in the Madison Lake Area. Include actual ice duration values and some representation of summary stats for each lake.
```{r}
ggplot(ice_duration_data, aes(x = lakeid, y = ice_duration)) +
  geom_jitter(width = 0.2, color = "purple") +
  geom_boxplot(fill = NA, width = 0.3, outlier.color = NA)
  
```

```{r}
madison_mean_ice_cover <- ice_duration_data |> 
  group_by(year4) |> 
  summarize(mean_duration = mean(ice_duration, na.rm = TRUE))

ggplot(data = madison_mean_ice_cover, aes(x = year4, y = mean_duration, color = mean_duration)) +
  geom_jitter() +
  labs(x = "Year", y = "Ice Mean Duration (days)") +
  theme_spongeBob(title.font = "SpongeBob")
```

This plot depicts how long a lake has been completely covered by ice from 1851 to 2019. The general trend is a slight decrease in the average of the lakes' total days that they are frozen over. 


### Air temp data

Find the mean air temp
```{r}
air_mean <- meteorological_data |> 
  filter(month %in% c(1, 2, 12)) |> 
  group_by(year4) |> 
  summarize( mean_air = mean(ave_air_temp_adjusted, na.rm = TRUE))
```

Create a visualization
```{r}

ggplot(data = air_mean, aes(x = year4, y = mean_air, color = mean_air)) +
  geom_point() +
  labs(x = "Year", y = " Mean air temp")
```
This plot depicts the mean air temperature for Maidson Lake by year. The trend is 